### 2012-03-19 docs/NewBCRobustness_paper/paper.tex
committing modified changes to paper (adding figs, adding discontinuous inflow section
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@380 36274a68-8941-4c93-80ef-affaed5139da

\subsection{Setting just $u_0$, not $u_0-\sigma_n$}

In practice, we will not have prior knowledge of $\sigma_n$ at the inflow, and will have to set $\beta_n u - \sigma_n = u_0$, ignoring the viscous contribution to the boundary condition.  The hope is that for small $\epsilon$, this omission will be negligible.

\subsection{Near discontinuous hat}

We note also that an additional advantage of selecting this new boundary condition is a relaxation of regularity requirements; strictly discontinuous inflow boundary conditions are no longer ``variational crimes".

>>>>

\subsection{Neglecting $\sigma_n$}

In practice, we will not have prior knowledge of $\sigma_n$ at the inflow, and will have to set $\beta_n u - \sigma_n = u_0$, ignoring the viscous contribution to the boundary condition.  The hope is that for small $\epsilon$, this omission will be negligible. Figure~\ref{ratios_noSigma} indicates that, between $\epsilon = .005$ and $\epsilon = .001$, the omission of $\sigma_n$ in the boundary condition becomes negligible, and both our error rates and ratios of $L^2$ to energy error become identical to the case where $\sigma_n$ is explicitly accounted for, well within the range of $\epsilon$ of physical interest. However, even for large $\epsilon = .01$, the $L^2$ error stagnates around $1e-3$, which is only $7%$ relative error.

\begin{figure}[h!]
\centering
\subfigure{
\includegraphics[scale=.38]{figs/rates_noSigma.png}
}
\subfigure{
\includegraphics[scale=.38]{figs/ratio_noSigma.png}
}
\caption{$L^2$ and energy errors, and their ratio for $\epsilon=.01$, $\epsilon=.005$, $\epsilon=.001$, $\epsilon=.0001$}
\label{ratios_noSigma}
\end{figure}

\subsection{Discontinuous inflow data}

We note also that an additional advantage of selecting this new boundary condition is a relaxation of regularity requirements; as $\widehat{f}_n \in H^{-1/2}(\Omega)$, strictly discontinuous inflow boundary conditions are no longer ``variational crimes".  We use the discontinuous inflow data
\[
u_0(y) = \begin{cases}
(y-1)^2&, \quad y>.5\\
y^2&, \quad y\leq .5 
\end{cases}
\]
